Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-21 PAPER.tex
Answer Adrian's _questions_ in Appendix B.

Formally we can express our test as: ``What is the $P_{\rm in}$ such that
\begin{equation}
\widehat{\textbf{p}}_{r} > \widehat{\textbf{p}}_{x} \Lambda,
\end{equation}  
where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e. the null test) the same.

 \begin{equation}
\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_r,P_{in}) dr
 \end{equation}
 where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_r,P_{in})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.

Probability vs. injection level is shown in Figure \ref{fig:Prob_vs_Pin}. At low injection levels the variation between $\textbf{x}$ and $\textbf{r}$ is such that the null test is ruled out to within $20$\%. This is the level expected from two distributions with $\sim$10 effective samples. 
%\dcj{checked with a little python test but needs a cite} 
As the injected signal approaches the level of the data, the probability of null rejection rises steeply.

>>>>

Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of "data + 
injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 
In other words, what is $e$ such that,
\begin{equation}
\widehat{\textbf{p}}_{e+x} > \widehat{\textbf{p}}_{x},
\end{equation}  
?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e. the null test) the same.

 \begin{equation}
\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) x
 \end{equation}
 where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.

Probability vs. injection level is shown in Figure \ref{fig:Prob_vs_Pin}. At low injection levels the variation between $\textbf{x}$ and $\textbf{(e+x)}$ is such that the null test is ruled out to within $20$\%. This is the level expected from two distributions with $\sim$10 effective samples. 
As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
